---
title: "Overview of UFO package and usage"
author: "K. Stewart"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

The UFO package includes two functions that one can use to retrieve data from the [National UFO Reporting Center (NUFORC) website](http://www.nwlink.com/~ufocntr/). The data for the reported sightings are grouped by area (province/state/territory) and are stored in separate html pages. The two letter code passed to the `area` argument specify from which html page to retrieve the reported sightings.

### `latest.sightings`

Primarily, one can use the function `latest.sightings` to find the 5 most recent reports of UFO's in the specified state, province or territory. The area is specified using two letters (e.g., BC for British Columbia, NY for New York). The number of reports can also be altered by passing a number to the `return.rows` argument. If you only want to see the most recent report, you can specify that with `return.rows = 1`. You could also retrieve all reports for the specified area by passing a very large number to `return.rows` (i.e., > 5000) if, for instance, you wished to summarize the reports differently.

For example, simply calling `latest.sightings()` will return the latest 5 reports from British Columbia, below.


```{r results='asis', echo=FALSE}
suppressPackageStartupMessages(library(dplyr))
library(ggplot2)
knitr::kable(UFO::latest.sightings())
```


Alternatively, calling `latest.sightings(area = 'NY', return.rows = 1)` will retrieve the latest report from New York state.


```{r results='asis', echo=FALSE}
knitr::kable(UFO::latest.sightings(area = 'NY', return.rows = 1))
```


*Special case!* passing `''` to `area` will return internationally reported sightings.


### `sightings.by.shape`

The other function in the UFO package returns either a ggplot or table of the frequency of shapes reported. As with `latest.sightings()`, one specifies the area with a two-letter code (default is 'BC'). The desired returned output is specified by passing either 'table' or 'plot to the `print` argument ('plot' is the default).

For example, `sightings.by.shape()` will return a barplot of the reported shape frequencies for British Columbia.



```{r echo=FALSE, fig.align='center', fig.height=7, fig.width=7}
UFO::sightings.by.shape()
```



Another example, returning a table of frequencies for California.



```{r results='asis', echo=FALSE}
knitr::kable(UFO::sightings.by.shape(area = 'CA', print = 'table'))
```

